Study of Intra- and Inter-Job Interference with Different Job Allocations

### 2016-07-10 discussion.tex
pass on discussion

The results shown in the previous section provide insights for the design of smart and flexible job allocation. By scrutinizing job's communication behavior, we can identify job's dominant communication pattern and pinpoint the ``neighborhood communication". With such knowledge about jobs' communication patterns, we can analyze the possible interference between jobs and take precautions to alleviate the negative effect when making allocation decisions.

@@

Not every application's preferable resource are compact node allocation and exclusive network provision. As we found in our analysis, applications whose dominant communication patterns contain intensive ``neighborhood communication" like ``Nearest Neighbor" don't benefit from compact node allocation and exclusive network provision. Applications, such as AMG, can run with non-contiguous node allocation without performance degradation, as long as the allocation unit can accommodate their ``neighborhood communication".

The allocation unit size shouldn't be fixed. Instead, the scheduler should choose a proper unit size based on the scale of ``neighborhood communication" of each job. The best unit size should be neither too big nor too small, jut perfectly fit for the size of that ``neighborhood". Big unit size won't be fully utilized and also cause fragmentation. Small unit size won't be able to accommodate the ``neighborhood communication" and makes the intra-job communication less efficient.

The advantage of making allocation with consideration about job's communication pattern is obvious. First, compared with contiguous allocation policy, the new scheduler outlined above is more flexible, without requiring the system to provide a big contiguous partition to accommodate the whole application, it only needs to provide a small set of compact nodes that is sufficient for all the "local community" in the application. On the other hand, the new scheduler outlined above won't destroy the locality of application's communication pattern. Indeed, the small compact node set (allocation unit) provided for the application's  ``local communities" can preserve the communication locality in the maximum extent. The design of such a smart scheduler is part of our future work.

>>>>

The results shown in the previous section provide insights 
for the design of smart and flexible job placement policy. 
By scrutinizing job's communication behavior, 
we can identify job's dominant communication pattern 
and pinpoint the ``neighborhood communication". 
With such knowledge about jobs' communication patterns, 
we can analyze the possible interference between jobs and 
take precautions to alleviate the negative effect when making placement decisions.

@@

Not every application's preferable resource are compact node allocation 
and exclusive network provision. 
As we demonstrate in our analysis, 
applications whose dominant communication pattern contains intensive 
``neighborhood communication" like ``Nearest Neighbor" do not benefit 
from compact node allocation and exclusive network provision. 
Applications, such as AMG, can run with non-contiguous node 
allocation without performance degradation, 
as long as the allocation unit can accommodate their ``neighborhood communication".

The allocation unit size shouldn't be fixed. 
Instead, the scheduler should choose a proper unit size 
based on the scale of ``neighborhood communication" of each job. 
The best unit size should be neither too big nor too small, 
just perfectly fit for the size of that ``neighborhood". 
Big unit size can not be fully utilized and thus cause fragmentation. 
Small unit size will not be able to accommodate the ``neighborhood communication", 
making the intra-job communication less efficient.

The advantage of making job placement with consideration about job's communication pattern is obvious. 
First, compared with contiguous allocation policy, 
the new scheduler with job's communication pattern awareness can be more flexible, 
without requiring the system to provide a big contiguous partition to accommodate the whole application, 
it only needs to provide a small set of compact nodes that is 
sufficient for all the "local community" in the application. 
On the other hand, 
the new scheduler is able to preserve the locality of application's communication pattern. 
Indeed, the small compact node set (allocation unit) provided for the application's 
``local communities" can preserve the communication locality in the maximum extent. 
The design of such a new scheduler with job communication pattern awareness 
is part of our future work.

### 2016-07-10 related_work.tex
pass on discussion

There are many tools available for system monitoring and application profiling. Tools like TAU (Tuning and Analysis)~\cite{tau}, 
and mpiP~\cite{mpip} can capture application's runtime information about application's communication and computation in event traces. However, recognizing the patterns about application's communication from those traces requires substantial effort. There are a number of studies on the recognition and characterization of parallel application communication patterns. Oak Ridge National Laboratory has its ongoing project about developing a tool set named Oxbow, which can characterize the computation and communication behavior of scientific applications and benchmarks~\cite{oxbow}. In a recent work~\cite{roth}, the authors demonstrate a new approach to automatically characterizing parallel applications' communication behaviors.

>>>>

There are many tools available for system monitoring and application profiling. 
Tools like TAU (Tuning and Analysis)~\cite{tau} and mpiP~\cite{mpip} can capture 
application's runtime information and keep records in event traces. 
However, recognizing the patterns about application's communication from those traces requires substantial effort. There are a number of studies on the recognition and characterization of parallel application communication patterns. Oak Ridge National Laboratory has its ongoing project about developing a tool set named Oxbow, which can characterize the computation and communication behavior of scientific applications and benchmarks~\cite{oxbow}. In a recent work~\cite{roth}, the authors demonstrate a new approach to automatically characterizing parallel applications' communication behaviors.
